Comparison of Fast, Hybird Imaging Architectures for Multi-scale, Hierarchical Aperture Arrays

### 2024-06-20 ms.tex
Update on Overleaf.

In transient search and cosmological applications, there will be additional processing required. For example, a de-dispersion trial process is required to discover new FRBs and pulsars with optimal signal-to-noise ratio. Computationally efficient algorithms for de-dispersion like the Fast Dispersion Measure Transform \citep[FDMT;][]{Zackay+2014} need to be performed on every independent pixel in the image formed. In intensity mapping applications for cosmology, the images need to be post-processed for deconvolution, foreground, removal, etc. As these post-processing computations are additional and common to all architectures, including them in our cost metric will not affect the results.

>>>>

In transient search and cosmological applications, there will be additional processing required. For example, a de-dispersion trial process is required to discover new FRBs and pulsars with optimal signal-to-noise ratio. Computationally efficient algorithms for de-dispersion like the Fast Dispersion Measure Transform \citep[FDMT;][]{Zackay+2014} need to be performed on every independent pixel in the image formed. In intensity mapping applications for cosmology, the images need to be post-processed for deconvolution, foreground, removal, etc. As these post-processing computations are additional and common to all architectures, including them in our cost metric will not affect the results. Calibration is another aspect that we have not included in our computational cost analysis. Because calibration typically operates on a significantly slower cadence compared to $t_\textrm{acc}$, and the computational cost is not tedious \citep{Beardsley+2017}, its contribution is negligible in the overall cost budget, and therefore will not affect the results.
